### 2018-07-13 paper/sphinxes.tex
Sphinxes: minor edits
Sphinxes: removes figures

  \item \(\ProcessHeader\) is the algorithm for processing incoming messages, 
    the processing is identical to Sphinx~\cite[\S 3.6, \S 3.7]{Sphinx} but 
    uses a different interface.
\end{itemize}

@@

First we generate all the needed keys.
We compute \(\nu+1\) tuples
\begin{align*}
  \alpha_0 &\gets g^\sk,
  & \secret_0 &\gets \bin^\kappa,
  & \blind_0 &\gets \hash_\blind(\alpha_0, \secret_0) \\
  \alpha_1 &\gets g^{\sk\blind_0},
  & \secret_1 &\gets \bin^\kappa,
  & \blind_1 &\gets \hash_\blind(\alpha_1, \secret_1) \\
  &\vdots &&\vdots && \vdots \\
  \alpha_\nu &\gets g^{\sk \blind_0\dotsb \blind_{\nu-1}},
  & \secret_\nu &\gets \bin^\kappa,
  & \blind_\nu &\gets \hash_\blind(\alpha_\nu, s_\nu).
\end{align*}
In addition, we compute
\begin{align*}
  \secret_0^{(0)} &\gets \pk_{n_0^{(0)}}^\sk,
  & \dotsc, &
  & \secret_0^{(|L_0|-1)} &\gets \pk_{n_0^{(|L_0|-1)}}^\sk \\
  \secret_1^{(0)} &\gets \pk_{n_1^{(0)}}^{\sk \blind_0},
  & \dotsc, &
  & \secret_1^{(|L_1|-1)} &\gets \pk_{n_1^{(|L_1|-1)}}^{\sk \blind_0} \\
  & \vdots &&& \vdots \\
  \secret_\nu^{(0)} &\gets \pk_{n_\nu^{(0)}}^{\sk \blind_0\dotsb 
    \blind_{\nu-1}},
  & \dotsc, &
  & \secret_\nu^{(|L_\nu|-1)} &\gets \pk_{n_\nu^{(|L_\nu|-1)}}^{\sk 
    \blind_0\dotsb \blind_{\nu-1}}.
\end{align*}
We note that a node \(n_i^{(j)}\) can compute \(s_i^{(j)}\) since \[
  s_i^{(j)} = \pk_{n_i^{(j)}}^{\sk \blind_0\dotsb \blind_{i-1}} = 
  \alpha_i^{\sk_{n_i^{(j)}}}.
\]
We then construct the ciphertexts
\begin{align*}
  C_0 &= \prp'\left(\hash_{\prp'}\left(s_0^{(0)}\right), s_0\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_0^{(|L_0|-1)}\right), s_0\right) \\
  C_1 &= \prp'\left(\hash_{\prp'}\left(s_1^{(0)}\right), s_1\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_1^{(|L_1|-1)}\right), s_1\right) \\
  & \vdots \\
  C_\nu &= \prp'\left(\hash_{\prp'}\left(s_\nu^{(0)}\right), s_\nu\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_\nu^{(|L_\nu|-1)}\right) 
    s_\nu\right).
\end{align*}
and pad them to \(w_L\kappa\) bits with uniformly random bits.
These computations are summarized in \cref{fig:SphinxesKeys}.
\commentDaniel{We can probably comment out the figure.}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \footnotesize
  \begin{algorithmic}[1]
    \Function{\ComputeKeys}{$L = \{L_0, \dotsc, L_l\}, w_L$}
      \State $\sk\rgets \ZZ_q^*, \pk\gets g^\sk$
      \State $\alpha_0\gets \pk$
      \State $s_0\rgets \bin^\kappa$
      \For{$1\leq i\leq |N_0|$}
        \State $s_0^{(i)}\gets \pk_{n_i}^\sk$, where $n_i\in |N_0|$.
        \State $c_0^{(i)}\gets \Enc[_{s_0^{(i)}}][s_0]$
      \EndFor
      \For{$|N_0|+1\leq i\leq w_L$}
        \State $c_0^{(i)}\rgets \bin^\kappa$
      \EndFor
      \State $C_0\gets (c_0^{(1)}, \dotsc, c_0^{(w)})$
      \State $b_0\gets \hash_\blind(\alpha_0, s_0)$
      \For{$1\leq i < \nu$}
        \State Compute $(\alpha_i, C_i, \beta_i, \gamma_i)$ as follows.
        \State $\alpha_i = \pk^{b_{i-1}}$
        \State $s_i\rgets \bin^\kappa$
        \For{$1\leq j\leq |N_i|$}
          \State $s_i^{(j)}\gets \pk_{n_j}^\sk$, where $n_j\in |N_i|$.
          \State $c_i^{(j)}\gets \Enc[_{s_i^{(j)}}][s_i]$
        \EndFor
        \For{$|N_i|+1\leq i\leq w_L$}
          \State $c_0^{(i)}\rgets \bin^\kappa$
        \EndFor
        \State $C_i\gets (c_i^{(1)}, \dotsc, c_i^{(w)})$
        \State $b_i\gets \hash_\blind(\alpha_i, s_i)$
      \EndFor
      \State \Return $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, 
      C_\nu, b_\nu)$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:SphinxesKeys}%
    A function computing the keys for all nodes on all layers of a route.
    \(L = \{L_i\}_i\) is the set of layers and each \(L_i\) is a set of the 
    nodes on that layer.
    \(w_L = \max_{L_i\in L} |L_i|\) is the maximum layer width, \ie the number 
    of nodes in the layer with most nodes.
  }
\end{figure}

Next we need to compute the padding \(\phi_i\) for each layer \(i\).
We must do this is to predict the padding introduced at each layer so that we 
can compute the correct \acp{MAC} (\(\gamma_i\)).
The padding for the outmost layer (layer 0) is the empty string, thus \(\phi_0 
  \gets \epsilon\).
Then, for layers \(1\leq i\leq \nu\), we get
\begin{multline*}
  \phi_i\gets \left\{\phi_{i-1}\concat 0_{w_H\kappa}\right\}\oplus \\
  \left\{\prg\left(\hash_\prg\left(s_{i-1}\right)\right)_{[(w_H(r-i)+3)\kappa..(2r+3)\kappa-1]}\right\}.
\end{multline*}
These computations are summarized in \cref{fig:SphinxesPadding}.
\commentDaniel{We can probably remove the figure.}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \footnotesize
  \begin{algorithmic}[1]
    \Function{\ComputePadding}{$\{s_0, \dotsc, s_\nu\}, w_H$}
      \State $\phi_0\gets \epsilon$
      \Comment{$\epsilon$ is the empty string.}
      \For{$1\leq i\leq \nu$}
        \State $\phi_i = \{ \phi_{i-1}\concat 0_{w_H} \} \oplus
          \{ \prg(\hash_\prg(s_{i-1}))_{[(w_H(r-i)+3)\kappa..(w_H 
            r+3)\kappa-1]} \}$
      \EndFor
      \State \Return $\phi_0, \dotsc, \phi_\nu$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:SphinxesPadding}%
    A function computing the needed padding.
    \(\{s_i\}_i\) is the set of keys for the layers.
    \(w_H\) is the width of the header at each layer, \ie everything that must 
    be removed and compensated by padding.
  }
\end{figure}

Next we will use the above computations to compute the mix headers \(M_i = 
  (\alpha_i, \beta_i, \gamma_i)\).
\(\alpha_i\) was computed above, so we will compute \(\beta_i\) and 
\(\gamma_i\).
We must compute \(\beta_i\) in reverse order.
We let \(\beta_{\nu+1} = I\concat 0_{(w_H r-1)\kappa}\), then, for \(\nu\leq 
  i\leq 0\), we let
\begin{align*}
  \beta_i &\gets \left\{L_{i+1}\concat \gamma_{i+1}\concat 
    (\beta_{i+1})_{[0..(w_H r-1)\kappa-1]}\right\}, \\
  \gamma_i &\gets \mac\left( \hash_\mac\left(s_i\right), \beta_i \right).
\end{align*}
The algorithm \(\CreateHeader\) is summarized in \cref{fig:CreateHeader}.
\commentDaniel{We can probably remove the figure.}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \footnotesize
  \begin{algorithmic}[1]
    \Function{\CreateHeader}{$I, L = \{L_i\}_i, w_L$}
      \State $w_H\gets (2w_L+1)$
      \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 
      b_\nu)\gets \ComputeKeys[L, w_L]$
      \State $\phi_0, \dotsc, \phi_\nu\gets \ComputePadding[\{s_0, \dotsc, 
      s_\nu\}, w_H]$
      \State $\alpha \gets \alpha_\nu$
      \State $C\gets C_\nu$
      \State $\beta \gets
        \left\{\left\{L_\nu\concat
            I\concat
            0_{(2w_L(r-\nu)+2)\kappa}\right\} \oplus
          \prg(\hash_\prg(s_\nu)_{[0..(2w_L(r-\nu)+3)\kappa-1]}\right\}\concat 
        \phi_\nu$
      \Comment{$\beta_\nu$}
      \State $\gamma \gets \mac(\hash_\mac(s_\nu), \beta)$
      \Comment{$\gamma_\nu$}
      \For{$\nu-1\leq i\leq 0$}
          \State $\beta_i \gets \{L_{i+1}, \concat \gamma_{i+1}\concat 
          (\beta_{i+1})_{[0..(w_L r-1)\kappa -1]}\}$
          \State $\gamma_i \gets \mac(\hash_\mac(s_i), \beta_i)$
      \EndFor
      \State \Return $(\alpha, C, \beta, \gamma), \{s_0, \dotsc, s_\nu\}$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:CreateHeader}%
    \dots
      $I\in \bin^\kappa$ is an identifier.
      $L = \{L_0, \dotsc, L_\nu\}$ such that $L_i, L_j\subset \N$, $L_i\cap L_j 
      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
      $L_\nu$ is the destination.
  }
\end{figure}

>>>>

  \item \(\ProcessHeader\) is the algorithm for processing incoming messages.
\end{itemize}

@@

First we generate all the needed keys.
We compute \(\nu+1\) tuples
\begin{align*}
  \alpha_0 &\gets g^\sk,
  & \secret_0 &\gets \bin^\kappa,
  & \blind_0 &\gets \hash_\blind(\alpha_0, \secret_0) \\
  \alpha_1 &\gets g^{\sk\blind_0},
  & \secret_1 &\gets \bin^\kappa,
  & \blind_1 &\gets \hash_\blind(\alpha_1, \secret_1) \\
  &\vdots &&\vdots && \vdots \\
  \alpha_\nu &\gets g^{\sk \blind_0\dotsb \blind_{\nu-1}},
  & \secret_\nu &\gets \bin^\kappa,
  & \blind_\nu &\gets \hash_\blind(\alpha_\nu, s_\nu).
\end{align*}
In addition, we compute
\begin{align*}
  \secret_0^{(0)} &\gets \pk_{n_0^{(0)}}^\sk,
  & \dotsc, &
  & \secret_0^{(|L_0|-1)} &\gets \pk_{n_0^{(|L_0|-1)}}^\sk \\
  \secret_1^{(0)} &\gets \pk_{n_1^{(0)}}^{\sk \blind_0},
  & \dotsc, &
  & \secret_1^{(|L_1|-1)} &\gets \pk_{n_1^{(|L_1|-1)}}^{\sk \blind_0} \\
  & \vdots &&& \vdots \\
  \secret_\nu^{(0)} &\gets \pk_{n_\nu^{(0)}}^{\sk \blind_0\dotsb 
    \blind_{\nu-1}},
  & \dotsc, &
  & \secret_\nu^{(|L_\nu|-1)} &\gets \pk_{n_\nu^{(|L_\nu|-1)}}^{\sk 
    \blind_0\dotsb \blind_{\nu-1}}.
\end{align*}
We note that a node \(n_i^{(j)}\) can compute \(s_i^{(j)}\) since \[
  s_i^{(j)} = \pk_{n_i^{(j)}}^{\sk \blind_0\dotsb \blind_{i-1}} = 
  \alpha_i^{\sk_{n_i^{(j)}}}.
\]
We then construct the ciphertexts
\begin{align*}
  C_0 &= \prp'\left(\hash_{\prp'}\left(s_0^{(0)}\right), s_0\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_0^{(|L_0|-1)}\right), s_0\right) \\
  C_1 &= \prp'\left(\hash_{\prp'}\left(s_1^{(0)}\right), s_1\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_1^{(|L_1|-1)}\right), s_1\right) \\
  & \vdots \\
  C_\nu &= \prp'\left(\hash_{\prp'}\left(s_\nu^{(0)}\right), s_\nu\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_\nu^{(|L_\nu|-1)}\right) 
    s_\nu\right).
\end{align*}
and pad them to \(w_L\kappa\) bits with uniformly random bits.

Next we need to compute the padding \(\phi_i\) for each layer \(i\).
We must do this is to predict the padding introduced at each layer so that we 
can compute the correct \acp{MAC} (\(\gamma_i\)).
The padding for the outmost layer (layer 0) is the empty string, thus \(\phi_0 
  \gets \epsilon\).
Then, for layers \(1\leq i\leq \nu\), we get
\begin{multline*}
  \phi_i\gets \left\{\phi_{i-1}\concat 0_{w_H\kappa}\right\}\oplus \\
  \left\{\prg\left(\hash_\prg\left(s_{i-1}\right)\right)_{[(w_H(r-i)+3)\kappa..(2r+3)\kappa-1]}\right\}.
\end{multline*}

Next we will use the above computations to compute the mix headers \(M_i = 
  (\alpha_i, \beta_i, \gamma_i)\).
\(\alpha_i\) was computed above, so we will compute \(\beta_i\) and 
\(\gamma_i\).
We must compute \(\beta_i\) in reverse order.
We let \(\beta_{\nu+1} = I\concat 0_{(w_H r-1)\kappa}\), then, for \(\nu\leq 
  i\leq 0\), we let
\begin{align*}
  \beta_i &\gets \left\{L_{i+1}\concat \gamma_{i+1}\concat 
    (\beta_{i+1})_{[0..(w_H r-1)\kappa-1]}\right\}, \\
  \gamma_i &\gets \mac\left( \hash_\mac\left(s_i\right), \beta_i \right).
\end{align*}
